### 2023-01-30 files/Chapter7/Beam.tex
Redoing code in python

\documentclass[../../main.tex]{subfiles}
\begin{document}
\section{Validity of the Timoshenko beam model}
This section is a literature study of the article \cite{LVV09}. The goal of \cite{LVV09} to show that the one-dimensional Timoshenko beam theory, is a feasible model to use in practical applications of beams. In the real world, a beam is a three-dimensional model. Therefore it is important to validate the use of the Timoshenko beam theory in practical applications.\\

@@

\section{Validity of the two-dimensional elastic model}
In this section, the validity of a two-dimensional cantilever beam is investigated. A three-dimensional cantilever beam is the model we'll use the measure. Recall that the two-dimensional model is an intermediate step between a Timoshenko beam and a three-dimensional beam.\\

In Chapter 1, models for a two-dimensional cantilever elastic body, as well as a three-dimensional cantilever elastic body is given. In Chapter 5, the Finite Element Method is applied to these models to obtain a formula to numerically calculate the eigenvalues and eigenfunctions of each of the models.\\

This section follows the same strategy as the previous section by comparing the eigenvalues and eigenfunctions of the models to determine the validity of the two-dimensional model. This investigation remains focussed on beam type problems.

>>>>

\documentclass[../../main.tex]{subfiles}
\begin{document}
\section{Validity of the Timoshenko beam model}
This section is a literature study of the article \cite{LVV09}. The goal of \cite{LVV09} to show that the one-dimensional Timoshenko beam theory, is a feasible model to use in practical applications of beams. In the real world, a beam is a complex three-dimensional model. Therefore it is important to validate the accuracy of a simlified theory like the Timoshenko beam theory for practical applications.\\

@@

\section{Validity of the two-dimensional elastic model}
In this section, the validity of a two-dimensional cantilever beam is investigated. This is a natural extension of the work in \cite{LVV09}. The authors mentioned this.\\

The model that will be considered is the two-dimensional elastic body defined in Chapter 1. The investigation will focus on the results relating to beam type problems.

and eigenfunctions of the models to determine the validity of the two-dimensional model. This investigation remains focussed on beam type problems.
